---
title: "Lab 1 - Reproducible research with RMarkdown and Github"
author: "Yoona Kwon"
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: kable
    fig_caption: no
    number_sections: no
    dev: pdf
    highlight: tango
  html_document:
    theme: paper
    toc: no
    df_print: kable
    fig_caption: no
    number_sections: no
    smart: yes
    dev: svg
    highlight: tango
    self_contained: true
  github_document:
    toc: true
    toc_depth: 4
    dev: svg
    df_print: kable
    html_preview: false
---

```{r setup, include=FALSE}
# DO NOT ALTER CODE IN THIS CHUNK
# Set knitr options
knitr::opts_chunk$set(
  echo = TRUE, eval = TRUE, fig.width = 5,
  fig.asp = 0.618, out.width = "80%", dpi = 120,
  fig.align = "center", cache = FALSE
)
# Load packages
suppressPackageStartupMessages(library(tidyverse))
```

---

## Exercise 1

Symbols ## and #### are used differently on the text. First, ## are used as Header2. Second, #### are used as Header 4, which has the small size font compared to two ##.


## Exercise 2

*What happens when you surround text with one-star pairs?*

-> The font is changed italic style.

**What happens when you surround text with two-star pairs?**

-> Two stars are making font bold.

***What happens when you surround text with three-star pairs?***

-> Three stars have italic and bold effect.


1.  Start typing this list. Note there are two spaces between the period 
    and the word "Start".
    
2.  Type the second line of the list

1.  What happens if I type step 3 as another step 1?

    -> It naturally changed to 3.

[What does this do?](https://google.com)

-> This work as a hyperlink. 
        
![How is this different from the above?]


## Exercise 3

| Column 1 | Column 2 | Column 3 | Column 4 |
| --- | ---: | :---: | :--- |
| Notice | what | the | colons |
| are | doing? | | |

Table: The table with poor spacing

| Column 1 | Column 2 | Column 3 | Column 4 |
| -------- | -------: | :------: | :------- |
| Notice   | what     | the      | colons   |
| are      | doing?   |          |          |

Table: The table with good spacing

## Exercise 4

| Column 1 | Column 2 | Column 3 | Column 4 | Column 5 |
| -------- | -------: | :------: | :------- |:------- |
| Notice   | what     | the      | colons   |CDS 101  |
| are      | doing?   |          |          |CDS 102  |


## Exercise 5

```{r}
qplot(x = displ, y = hwy, data = mpg)
```



## Exercise 6

```{r}
print(mpg)
```

